---
title: "EDA Alfonso"
author: "Alfonso Rojas-Alvarez"
date: "4/6/2022"
output: html_document
---


```{r cars}
### EDA and modeling
library(ggplot2)
library(dplyr)
library(fixest)
library(factoextra)
comp <- read.csv("full.csv")
```

Lives Alone is widely varying between groups

```{r}
table(comp$lives_alone, comp$group)
```

Let's check now only undergrads. 

```{r}
col_samp <- comp %>%
  filter(educ == 4)
table(col_samp$lives_alone, col_samp$group)

col_samp %>% filter(group == "National") %>%
  summarize(mean(lives_alone, na.rm= TRUE))

col_samp %>% filter(group == "PAGL") %>%
  summarize(mean(lives_alone, na.rm= TRUE))
t.test(col_samp$lives_alone, as.numeric(col_samp$group), na.rm = TRUE)
```
Interesting, so, the general college populaton lives alone more than just the UT/Mexico sample. This might be a matter of age. There aren't many old UT students while there should be a lot in the general population. Let's explore this:

```{r}
col_samp %>% 
  ggplot(aes(x=age, colour=group)) + geom_density() +
  labs(x = "Age", y = "Proportion", 
       title = "Age by Sample Group", fill = "group", subtitle= "PAGL, HPS 2021", 
       caption = "PAGL, University of Texas, 2021") +
  labs(color='Group') + theme(legend.position = c(0.8, 0.8)) + theme_bw()
```

Yeah, as expected.

Let's now look at anxiety levels.

```{r}

col_samp %>% 
  filter(group == "National") %>%
  filter(anxious > -0.1) %>%
  summarize(mean(anxious, na.rm= TRUE))

col_samp %>% filter(group == "PAGL") %>%
  filter(anxious > -0.1) %>%
  summarize(mean(anxious, na.rm= TRUE))

for_t <- col_samp %>%
  filter(anxious > -0.1)

t.test(for_t$anxious, as.numeric(for_t$group), na.rm = TRUE)
```

```{r}
col_samp %>% 
  filter(anxious > -0.1) %>%
  ggplot(aes(x=anxious, colour=group)) + geom_density() +
  labs(x = "Anxiety", y = "Proportion", 
       title = "Anxiety by Sample Group", fill = "group", subtitle= "PAGL, HPS 2021", 
       caption = "PAGL, University of Texas, 2021") +
  labs(color='Group') + theme(legend.position = c(0.8, 0.8)) + theme_bw()
```

```{r}
col_samp %>% 
  group_by(group) %>%
  filter(anxious > -0.1) %>%
  filter(had_covid > -0.1) %>%
  filter(employed > -0.1) %>%
  filter(prescription > -0.1) %>%
  filter(prescription > -0.1) %>%
  summarize(anxiety = mean(anxious, na.rm = TRUE), female = mean(female, na.rm = TRUE), hispanic = mean(hispanic, na.rm = TRUE), covid = mean(had_covid, na.rm = TRUE), employment = mean(employed, na.rm = TRUE), prescription = mean(prescription, na.rm = TRUE), age = mean(age, na.rm = TRUE))
```

Okay, the difference between groups looks pretty straightforward. Let's have some fun with regressions.

First let's select the regression sample, it has to be the one where no on has a missing:

```{r}
reg_samp <- col_samp %>% 
  select(anxious, group, had_covid, employed, prescription, age, female, hispanic, state) %>%
  filter(anxious > -0.1) %>%
  filter(had_covid > -0.1) %>%
  filter(employed > -0.1) %>%
  filter(prescription > -0.1)

reg_samp_comp <- comp %>% 
  select(anxious, educ, group, had_covid, employed, prescription, age, female, hispanic, state) %>%
  filter(anxious > -0.1) %>%
  filter(had_covid > -0.1) %>%
  filter(employed > -0.1) %>%
  filter(prescription > -0.1)
```

```{r}
reg_samp %>% 
  filter(group == "National") %>%
  filter(anxious > -0.1) %>%
  summarize(mean(anxious, na.rm= TRUE), n())

reg_samp %>% filter(group == "PAGL") %>%
  filter(anxious > -0.1) %>%
  summarize(mean(anxious, na.rm= TRUE), n())


```

```{r}
comp %>% 
  filter(group == "National") %>%
  filter(anxious > -0.1) %>%
  filter(prescription > -0.1) %>%
  summarize(mean(anxious, na.rm= TRUE), n())

comp %>% filter(group == "PAGL") %>%
  filter(prescription > -0.1) %>%
  filter(anxious > -0.1) %>%
  summarize(mean(anxious, na.rm= TRUE), n())


### Anxiety
basicanx_col<- feglm(anxious ~ group + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + factor(prescription) + age, data = reg_samp)
anx_full <- feglm(anxious ~ group + factor(educ) + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + factor(prescription) + age, data = reg_samp_comp)
####### Add state fixed effects
anxfe_full<- feglm(anxious ~ group + factor(educ) + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + factor(prescription) + age | state, data = reg_samp_comp)
anxfe_col <- feglm(anxious ~ group + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + factor(prescription) + age | state, data = reg_samp)

### Prescription
presc_col<- feglm(prescription ~ group + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + age, data = reg_samp, family = "binomial")
presc_full <- feglm(prescription ~ group + factor(educ) + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + age, data = reg_samp_comp, family = "binomial")
####### Add state fixed effects
prescanxfe_full<- feglm(prescription ~ group + factor(educ) + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + age | state, data = reg_samp_comp, family = "binomial")
prescanxfe_col <- feglm(prescription ~ group + factor(female) + factor(hispanic) + factor(had_covid) + factor(employed) + age | state, data = reg_samp, family = "binomial")

b <- etable(presc_col, presc_full, prescanxfe_full, prescanxfe_col)
```

### Let's do some segmentation to see if something interesting comes out of it.

```{r eval=FALSE, include=FALSE}
segmenting <- reg_samp %>% 
  select(-state, -anxious, -group) %>% 
  ungroup()
        
segmenting <- na.omit(segmenting)
set.seed(100)
km <- kmeans(segmenting,  centers = 4, nstart = 1)
fviz_cluster(km, data = segmenting, geom = "point",
             ellipse.type = "convex", 
             ggtheme = theme_bw()) + 
               scale_fill_discrete(name="Groups",
                                  breaks=c("1", "2", "3", "4"),
                                   labels=c("A", "B", "C", "D")) + 
  scale_colour_discrete(guide = "none") +
  scale_shape_discrete(guide = "none") + 
  labs(title="K-means segmentation of sample",
                              subtitle= "PAGL and HPS, 2022")
data.frame(km$centers)
```

```{r paged.print=FALSE}
a <- etable(basic_col, basic_full, fe_col, fe_full)
```