---
title: "SLAS PAGL Variables Cleaning"
author: "Melanie Milligan"
date: "3/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Reset
rm(list=ls())
library(tidyverse)
library(ggplot2)
```

## Variable Selection

```{r select-vars}
# Load English Data
file <- "C:/Users/Melanie/Documents/UT Austin/PAGL/SLAS/data_eng.csv"

# Read the English csv file
data_eng <- read.csv(file, header = TRUE) %>% 
  slice(-c(1, 2)) %>%
  # Select variables
  select(Progress, ResponseId, Q2, Q38:Q39, Q48:Q49_8_TEXT, Q41, Q85_1:Q85_3, Q35:Q37, Q46,
        Q28_1:Q28_18, Q92, Q29_1:Q29_6, Q42, Q28_19, Q4_12_TEXT, Q4_13_TEXT) %>%
  # Get rid of the test rows
  filter(Q4_12_TEXT != "MELANIE TEST" & Q4_12_TEXT != "MELANIETEST" & Q4_12_TEXT != "MELANIIETEST" &
           Q49_8_TEXT != "MELANIETEST" & Q49_8_TEXT != "MELANIE TEST") %>%
  select(-Q4_12_TEXT, -Q4_13_TEXT)

# Load Spanish Data
file2 <- "C:/Users/Melanie/Documents/UT Austin/PAGL/SLAS/data_span.csv"

#Read the Spanish csv file
data_span <- read.csv(file2, header = TRUE) %>%
  slice(-c(1, 2)) %>%
  # Select variables
  select(Progress, ResponseId, Q2, Q38:Q39, Q41, Q85, Q35:Q37, Q46, Q28_1:Q28_18, Q92,
         Q29_1:Q29_6, Q42, Q28_19)
```

## Naming the Variables

We'll start off by renaming the variables in the English data set.
```{r name-eng}
data_eng <- data_eng %>%
  rename(progress = Progress, responseID = ResponseId, university = Q2, age = Q38, gender = Q39,
        hispanic = Q48, race_amind = Q49_2, race_asian = Q49_3, race_haw = Q49_6,
        race_black = Q49_7, race_white = Q49_5, race_other = Q49_8, 
        race_other_text = Q49_8_TEXT, year = Q41, lives_alone = Q85_1, lives_roommates = Q85_2, 
        lives_family = Q85_3, had_covid = Q35, covid_symp = Q36, move_pandemic = Q37, 
        is_employed = Q46, PAS_teachers_critical = Q28_1, PAS_teachers_unrealistic = Q28_2, 
        PAS_parents_unrealistic = Q28_3, PAS_time = Q28_4, PAS_excessive_workload = Q28_5,
        PAS_amount_too_much = Q28_6, PAS_behind = Q28_7, PAS_relax = Q28_8, 
        PAS_exams_difficult = Q28_9, PAS_exams_time = Q28_10, PAS_exams_stressful = Q28_11,
        PAS_weakness = Q28_12, PAS_job = Q28_13, PAS_confident_student = Q28_14,
        PAS_confident_career = Q28_15,PAS_decisions_easy = Q28_16, PAS_fear_failing = Q28_17,
        PAS_intense_competition = Q28_18, overall_mental_health = Q92, 
        resources_counseling_inst = Q29_1, resources_medication = Q29_2,
        resources_wellness_inst = Q29_3, resources_counseling_noninst = Q29_4,
        resources_wellness_noninst = Q29_5, resources_informal = Q29_6, living_situation = Q42,
        financial_stress = Q28_19)
```

Next, we'll rename the variables in the Spanish data set

```{r name-span}
data_span <- data_span %>%
  rename(progress = Progress, responseID = ResponseId, university = Q2, age = Q38, gender = Q39,
        year = Q41, lives_with = Q85, had_covid = Q35, covid_symp = Q36, move_pandemic = Q37, 
        is_employed = Q46, PAS_teachers_critical = Q28_1, PAS_teachers_unrealistic = Q28_2, 
        PAS_parents_unrealistic = Q28_3, PAS_time = Q28_4, PAS_excessive_workload = Q28_5,
        PAS_amount_too_much = Q28_6, PAS_behind = Q28_7, PAS_relax = Q28_8, 
        PAS_exams_difficult = Q28_9, PAS_exams_time = Q28_10, PAS_exams_stressful = Q28_11,
        PAS_weakness = Q28_12, PAS_job = Q28_13, PAS_confident_student = Q28_14,
        PAS_confident_career = Q28_15,PAS_decisions_easy = Q28_16, PAS_fear_failing = Q28_17,
        PAS_intense_competition = Q28_18, overall_mental_health = Q92, 
        resources_counseling_inst = Q29_1, resources_medication = Q29_2,
        resources_wellness_inst = Q29_3, resources_counseling_noninst = Q29_4,
        resources_wellness_noninst = Q29_5, resources_informal = Q29_6, living_situation = Q42,
        financial_stress = Q28_19)
```

## Translating and Cleaning Variables
```{r translate}
# University
data_span$university <- recode(data_span$university, `UNAM (CU / CDMX)` = "UNAM", 
                               `Otro` = "Other")

# Gender
data_span$gender <- recode(data_span$gender, `Mujer` = "Female", `Hombre` = "Male",
                           `Prefiero no responder` = "Prefer not to say", 
                           `No binario` = "Nonbinary", `Otro (especificar):` = "Other")

# Year
data_span$year <- recode(data_span$year, `Primero` = "Freshman", `Segundo` = "Freshman",
                         `Tercero` = "Sophomore", `Cuatro` = "Sophomore", `Quinto` = "Junior",
                         `Sexto` = "Junior", `Séptimo` = "Senior", `Octavo` = "Senior",
                         `Más de octavo` = "Senior")

# Had Covid
data_span$had_covid <- recode(data_span$had_covid, `Sí` = "Yes")

# Covid Symptoms
data_span$covid_symp <- recode(data_span$covid_symp, `Ninguno (asintomático)` = "None (asymptomatic)",
                               `Muy leve` = "Very Mild", `Leve` = "Mild", `Moderado` = "Moderate",
                               `Severo` = "Severe")

# Who They Live With
data_span <- data_span %>%
  # Create a new column for each option to match English data set
  mutate("lives_alone" = ifelse(grepl("Solo(a)", data_span$lives_with), "Alone", -99)) %>%
  mutate("lives_roommates" = ifelse(grepl("Con compañeros de casa", 
                                          data_span$lives_with), "With roomate(s)", -99)) %>%
  mutate("lives_family" = ifelse(grepl("Con familia", data_span$lives_with),
                                 "With family", -99)) %>%
  # Remove original `lives_with` column
  select(-lives_with)

# Moved During Pandemic
data_span$move_pandemic <- recode(data_span$move_pandemic, `Sí` = "Yes")

# Employed
data_span$is_employed <- recode(data_span$is_employed, `Sí` = "Yes")

# Mental Health resources
data_span$resources_counseling_inst <- recode(data_span$resources_counseling_inst, `Sí` = "Yes")
data_span$resources_medication <- recode(data_span$resources_medication, `Sí` = "Yes")
data_span$resources_wellness_inst <- recode(data_span$resources_wellness_inst, `Sí` = "Yes")
data_span$resources_wellness_noninst <- recode(data_span$resources_wellness_noninst, `Sí` = "Yes")
data_span$resources_counseling_noninst <- recode(data_span$resources_counseling_noninst, `Sí` = "Yes")
data_span$resources_informal <- recode(data_span$resources_informal, `Sí` = "Yes")

# Overall mental health
data_span$overall_mental_health <- recode(data_span$overall_mental_health, `Mala` = "Poor",
                                          `Regular` = "Fair", `Buena` = "Good", 
                                          `Muy Buena` = "Very Good", `Excelente` = "Excellent")

# NOTE: We need to figure out a way to align `living_situation` with the English survey
```

Now, we'll clean the PAS variables so that they are numeric. Note that NA values will be transformed to values of 0 or below, so these will need to be removed in individual analyses!
```{r PAS}
# Function to use in clean_PAS functions to remove NAs
subtractby1 <- function(x) {
  x - 1
}

# Function to clean English items of PAS scale
clean_PAS_eng <- function(x) {
  x %>%
  factor(levels = (c("-99", "Strongly Disagree", "Disagree", # rename levels
                                      "Undecided", "Agree", "Strongly Agree"))) %>%
  as.numeric() %>% # convert to numeric
  subtractby1() #%>% # subtract each value by 1
}

# Clean English PAS Items (rc stands for reverse code)
data_eng$PAS_teachers_critical <- clean_PAS_eng(data_eng$PAS_teachers_critical)
data_eng$PAS_teachers_unrealistic <- clean_PAS_eng(data_eng$PAS_teachers_unrealistic)
data_eng$PAS_parents_unrealistic <- clean_PAS_eng(data_eng$PAS_parents_unrealistic)
data_eng$PAS_time <- car::recode(clean_PAS_eng(data_eng$PAS_time), "1=5; 2=4; 4=2; 5=1")  # rc
data_eng$PAS_excessive_workload <- clean_PAS_eng(data_eng$PAS_excessive_workload)
data_eng$PAS_amount_too_much <- clean_PAS_eng(data_eng$PAS_amount_too_much)
data_eng$PAS_behind <- clean_PAS_eng(data_eng$PAS_behind)
data_eng$PAS_relax <- car::recode(clean_PAS_eng(data_eng$PAS_relax), "1=5; 2=4; 4=2; 5=1") # rc
data_eng$PAS_exams_difficult <- clean_PAS_eng(data_eng$PAS_exams_difficult)
data_eng$PAS_exams_time <- clean_PAS_eng(data_eng$PAS_exams_time)
data_eng$PAS_exams_stressful <- clean_PAS_eng(data_eng$PAS_exams_stressful)
data_eng$PAS_weakness <- clean_PAS_eng(data_eng$PAS_weakness)
data_eng$PAS_job <- clean_PAS_eng(data_eng$PAS_job)
data_eng$PAS_confident_student <- car::recode(clean_PAS_eng(data_eng$PAS_confident_student), 
                                              "1=5; 2=4; 4=2; 5=1") # rc
data_eng$PAS_confident_career <- car::recode(clean_PAS_eng(data_eng$PAS_confident_career), 
                                             "1=5; 2=4; 4=2; 5=1") # rc
data_eng$PAS_decisions_easy <- car::recode(clean_PAS_eng(data_eng$PAS_decisions_easy), 
                                           "1=5; 2=4; 4=2; 5=1") # rc
data_eng$PAS_fear_failing <- clean_PAS_eng(data_eng$PAS_fear_failing)
data_eng$PAS_intense_competition <- clean_PAS_eng(data_eng$PAS_intense_competition)
data_eng$financial_stress <- clean_PAS_eng(data_eng$financial_stress)

# Function to clean Spanish PAS items
clean_PAS_span <- function(x) {
  x %>%
  factor(levels = (c("-99", "Totalmente en Desacuerdo", "En Desacuerdo", # rename levels
                                      "Neutral", "De Acuerdo", "Totalmente de Acuerdo",
                                     "N/A", "No Sé"))) %>%
  as.numeric() %>% # convert to numeric
  subtractby1() #%>% # subtract each value by 1
}

# Clean Spanish PAS Items (rc stands for reverse code)
data_span$PAS_teachers_critical <- clean_PAS_span(data_span$PAS_teachers_critical)
data_span$PAS_teachers_unrealistic <- clean_PAS_span(data_span$PAS_teachers_unrealistic)
data_span$PAS_parents_unrealistic <- clean_PAS_span(data_span$PAS_parents_unrealistic)
data_span$PAS_time <- car::recode(clean_PAS_span(data_span$PAS_time), "1=5; 2=4; 4=2; 5=1")  # rc
data_span$PAS_excessive_workload <- clean_PAS_span(data_span$PAS_excessive_workload)
data_span$PAS_amount_too_much <- clean_PAS_span(data_span$PAS_amount_too_much)
data_span$PAS_behind <- clean_PAS_span(data_span$PAS_behind)
data_span$PAS_relax <- car::recode(clean_PAS_span(data_span$PAS_relax), "1=5; 2=4; 4=2; 5=1") # rc
data_span$PAS_exams_difficult <- clean_PAS_span(data_span$PAS_exams_difficult)
data_span$PAS_exams_time <- clean_PAS_span(data_span$PAS_exams_time)
data_span$PAS_exams_stressful <- clean_PAS_span(data_span$PAS_exams_stressful)
data_span$PAS_weakness <- clean_PAS_span(data_span$PAS_weakness)
data_span$PAS_job <- clean_PAS_span(data_span$PAS_job)
data_span$PAS_confident_student <- car::recode(clean_PAS_span(data_span$PAS_confident_student), 
                                               "1=5; 2=4; 4=2; 5=1") # rc
data_span$PAS_confident_career <- car::recode(clean_PAS_span(data_span$PAS_confident_career), 
                                              "1=5; 2=4; 4=2; 5=1") # rc
data_span$PAS_decisions_easy <- car::recode(clean_PAS_span(data_span$PAS_decisions_easy), 
                                            "1=5; 2=4; 4=2; 5=1") # rc
data_span$PAS_fear_failing <- clean_PAS_span(data_span$PAS_fear_failing)
data_span$PAS_intense_competition <- clean_PAS_span(data_span$PAS_intense_competition)
data_span$financial_stress <- clean_PAS_span(data_span$financial_stress) 
```

## Merging the Data Sets
Now, we can finally merge the Spanish and English data sets!
```{r merge}
# Merge the English and Spanish Data Sets
df <- merge(data_eng, data_span, all = TRUE)

# Filter out rows where progress < 20
df <- df %>%
  subset(as.numeric(progress) > 19) %>%
  subset(university != "Other")
```

## Variables

### University
```{r university}
df$university <- as.factor(df$university)

table(df$university)

df %>%
  select(university) %>%
  ggplot(aes(x = university, fill = university)) + geom_bar(stat = "count") +
  labs(title = "Respondent Count by University")

print(str(df$university))
```
### Age
```{r age}
df$age <- as.numeric(df$age)

table(df$age)

df %>%
  select(age) %>%
  filter(age > 0) %>%
  ggplot(aes(x = age)) + geom_histogram(binwidth = 1, bins = 48, fill = I("blue"),alpha= I(.5)) +
  labs(title = "Respondent Ages")

print(str(df$age))
```
### Gender Identity
```{r gender}
df$gender <- as.factor(df$gender)

df$gender <- recode(df$gender, `Other (please specify):` = "Other")
  
table(df$gender)

df %>%
  select(gender) %>%
  filter(gender != -99, gender != "") %>%
  ggplot(aes(x = gender, fill = gender)) + geom_bar(stat = "count") +
  labs(title = "Respondent Genders")

print(str(df$gender))
```

### Academic Year
```{r year}
df$year <- as.factor(df$year)

table(df$year)

df %>%
  select(year) %>%
  filter(year != -99, year != "") %>%
  ggplot(aes(x = year, fill = year)) + geom_bar(stat = "count") +
  labs(title = "Respondent Academic Years")

print(str(df$year))
```

### Who they live with (NEED HELP)
```{r lives_with}
## I DON'T KNOW HOW TO DEAL WITH THIS VARIABLE
```

### Whether Respondent Had COVID-19
```{r had-covid}
df$had_covid <- as.factor(df$had_covid)

table(df$had_covid)

df %>%
  select(had_covid) %>%
  filter(had_covid != -99, had_covid != "") %>%
  ggplot(aes(x = had_covid, fill = had_covid)) + geom_bar(stat = "count") +
  labs(title = "Did Respondent Have COVID-19?")

print(str(df$had_covid))
```

### Severity of COVID-19 Symptoms
```{r covid_symptoms}
df$covid_symp <- as.factor(df$covid_symp)

table(df$covid_symp)

df %>%
  select(covid_symp) %>%
  filter(covid_symp != -99, covid_symp != "") %>%
  ggplot(aes(x = covid_symp, fill = covid_symp)) + geom_bar(stat = "count") +
  labs(title = "Severity of COVID-19 Symptoms (If Respondent Had COVID-19)") +
  theme(axis.text.x = element_text(angle = 90))

print(str(df$covid_symp))
```

### Whether Respondent Moved During Pandemic
```{r move_pandemic}
df$move_pandemic <- as.factor(df$move_pandemic)

table(df$move_pandemic)

df %>%
  select(move_pandemic) %>%
  filter(move_pandemic != -99, move_pandemic != "") %>%
  ggplot(aes(x = move_pandemic, fill = move_pandemic)) + geom_bar(stat = "count") +
  labs(title = "Did Respondent Move During Pandemic?")

print(str(df$move_pandemic))
```

### Employment
```{r is_employed}
df$is_employed <- as.factor(df$is_employed)

table(df$is_employed)

df %>%
  select(is_employed) %>%
  filter(is_employed != -99, is_employed != "") %>%
  ggplot(aes(x = is_employed, fill = is_employed)) + geom_bar(stat = "count") +
  labs(title = "Is Respondent Employed?")

print(str(df$is_employed))
```

### Mean PAS Score
```{r PAS_mean}
df <- df %>%
  # Create aggregate value of sum of all 18 PAS items
  mutate(PAS_sum = PAS_teachers_critical + PAS_teachers_unrealistic + PAS_parents_unrealistic +
           PAS_time + PAS_excessive_workload + PAS_amount_too_much + PAS_behind + PAS_relax + 
           PAS_exams_difficult + PAS_exams_time + PAS_exams_stressful + PAS_weakness + PAS_job + 
           PAS_confident_student + PAS_confident_career + PAS_decisions_easy + PAS_fear_failing + 
           PAS_intense_competition) %>%
  # Drop the NAs (we're going to divide next, which requires dropping NAs)
  drop_na(PAS_sum) %>%
  # Create aggregate value of mean PAS score for each respondent (there are 18 items in the scale)
  mutate(PAS_mean = PAS_sum / 18) %>%
  # Remove extraneous 0s (exist due to Qualtrics' classification of another type of NA)
  filter(PAS_mean != 0)

table(df$PAS_mean)

df %>%
  select(PAS_mean) %>%
  ggplot(aes(x = PAS_mean)) + geom_histogram(binwidth = .2, fill = I("blue"),alpha= I(.5)) +
  labs(title = "Distribution of Mean PAS Scores")
```

### Financial Stress
```{r financial-stress}
table(df$financial_stress)

df %>%
  select(financial_stress) %>%
  ggplot(aes(x = financial_stress)) + geom_histogram(binwidth = 1, fill = I("blue"),alpha= I(.5)) +
  labs(title = "Distribution of Financial Stress")

str(df$financial_stress)
```
### Overall Mental Health
```{r overall-mental-health}
df$overall_mental_health <- as.factor(df$overall_mental_health)

table(df$overall_mental_health)

df %>%
  select(overall_mental_health) %>%
  filter(overall_mental_health != -99, overall_mental_health != "") %>%
  ggplot(aes(x = overall_mental_health, fill = overall_mental_health)) + geom_bar(stat = "count") +
  labs(title = "Distribution of Overall Mental Health")

str(df$overall_mental_health)
```
### Mental Health Resources (6 Resources)
```{r mh1}
## counseling at university
df$resources_counseling_inst <- as.factor(df$resources_counseling_inst)

table(df$resources_counseling_inst)

df %>%
  select(resources_counseling_inst) %>%
  filter(resources_counseling_inst != -99, resources_counseling_inst != "") %>%
  ggplot(aes(x = resources_counseling_inst, fill = resources_counseling_inst)) + 
  geom_bar(stat = "count") +
  labs(title = "Received Counseling at University")


str(df$resources_counseling_inst)
```
````{r mh2}
## counseling outside university
df$resources_counseling_noninst <- as.factor(df$resources_counseling_noninst)

df %>%
  select(resources_counseling_noninst) %>%
  filter(resources_counseling_noninst != -99, resources_counseling_noninst != "") %>%
  ggplot(aes(x = resources_counseling_noninst, fill = resources_counseling_noninst)) + 
  geom_bar(stat = "count") +
  labs(title = "Received Counseling Outside University")

str(df$resources_counseling_noninst)
```

```{r mh3}
## medication
df$resources_medication <- as.factor(df$resources_medication)

df %>%
  select(resources_medication) %>%
  filter(resources_medication != -99, resources_medication != "") %>%
  ggplot(aes(x = resources_medication, fill = resources_medication)) + 
  geom_bar(stat = "count") +
  labs(title = "Received Psychiatric Medication Treatment")

str(df$resources_medication)
```


```{r mh4}
## wellness program at university
df$resources_wellness_inst <- as.factor(df$resources_wellness_inst)

df %>%
  select(resources_wellness_inst) %>%
  filter(resources_wellness_inst != -99, resources_wellness_inst != "") %>%
  ggplot(aes(x = resources_wellness_inst, fill = resources_wellness_inst)) + 
  geom_bar(stat = "count") +
  labs(title = "Participated in Wellness Program at University")

str(df$resources_wellness_inst)
```

```{r mh5}
## wellness program outside university
df$resources_wellness_noninst <- as.factor(df$resources_wellness_noninst)

df %>%
  select(resources_wellness_noninst) %>%
  filter(resources_wellness_noninst != -99, resources_wellness_noninst != "") %>%
  ggplot(aes(x = resources_wellness_noninst, fill = resources_wellness_noninst)) + 
  geom_bar(stat = "count") +
  labs(title = "Participated in Wellness Program Outside University")

str(df$resources_wellness_noninst)
```

```{r mh6}
## informal counseling
df$resources_informal <- as.factor(df$resources_informal)

df %>%
  select(resources_informal) %>%
  filter(resources_informal != -99, resources_informal != "") %>%
  ggplot(aes(x = resources_informal, fill = resources_informal)) + 
  geom_bar(stat = "count") +
  labs(title = "Received Informal Counseling")

str(df$resources_informal)
```

### Ethnicity
```{r ethnicity}
df$hispanic <- as.factor(df$hispanic)

table(df$hispanic)

df %>%
  select(hispanic) %>%
  filter(hispanic != -99, hispanic != "") %>%
  ggplot(aes(x = hispanic, fill = hispanic)) + 
  geom_bar(stat = "count") +
  labs(title = "Ethnicity (UT Students Only")

str(df$hispanic)
```

### Race (NEED HELP)